---
title: "Homework 1"
author: Jinghan Zhang
date: September 10, 2020
output: github_document
---

## Problem 1

Create a data frame comprised of:
-----------------------------------------------------------------------
* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
  library(tidyverse)
  problemone_df = tibble(
    vec_numeric = rnorm(10),
    vec_logical = c(vec_numeric > 0),
    vec_char = c("This", "is", "a", "long", "sentence", "to", "say", "nothing", "at", "all"),
    vec_factor = factor(c("sad", "angry", "happy", "angry", "sad", "sad", "sad", "happy", "angry", "angry"))
)
```

Try to take the mean of each variable in your dataframe. What works and what doesn’t?
**The variables for which I can take the mean are the random sample of double values and logical vector. It does not work for the char vector or factor vector.**

In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?

```{r, eval = FALSE}
  problemone_df %>% 
  summarise(as.numeric(vec_logical)) 
  problemone_df %>% 
  summarise(as.numeric(vec_char))
  problemone_df %>% 
  summarise(as.numeric(vec_factor))
```

**The logical and factor vectors are able to be converted. By applying as.numeric to the logical vector, a tibble of double values is generated with 0 for FALSE and 1 for TRUE. By applying as.numeric to the factor vector, a tibble of double values is generated with 1-3 for the corresponding factor "levels". However, there is an error for the char vector because there is no corresponding numeric value that can be assigned.**

In a second code chunk:
-----------------------------------------------------------------------
* convert the logical vector to numeric, and multiply the random sample by the result
* convert the logical vector to a factor, and multiply the random sample by the result
* convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r}
```

## Problem 2

```{r}
  data("penguins", package = "palmerpenguins")
```

Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:
-----------------------------------------------------------------------
* the data in this dataset, including names / values of important variables
* the size of the dataset (using nrow and ncol)
* the mean flipper length

Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).

Export your first scatterplot to your project directory using ggsave.
